Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-16 paper.tex
formatting

The remainder of this paper is organized as follows.
We begin by describing the target language we will analyze in Section~\ref{background},
including a concrete CESK machine as small-step operational semantics for it.
We continue with a review of abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines. Following this, Section~\ref{linear} shows a conversion from the
nondeterministic choices of closures to another layer of continuations,
therefore linearizing the abstract execution.
Section~\ref{fusing} then discusses fusing the driver and step functions to a single
function.
We further identify in Section~\ref{disen} the first-order data type representations of
continuations, and disentangle the code blocks for dispatching data types to separate
functions.
Section~\ref{refunc} then represents the refunctionalized abstract abstract machines.
In this section, the continuations represented by data types become higher-order
functions.
In Section~\ref{directstyle}, we transform the refunctionalized AAM to two
different direct style, one is implemented with monads, the other is using
delimited controls.

@@

\todo{Add section numbers to the figure}

@@

\begin{lstlisting}
e $\in$ Exp ::= ae
          | (let ([x (ae ae)]) e)
ae $\in$ AExp ::= x
            | lam
lam $\in$ Lam ::= (lambda (x) e)
x ... are variable names
\end{lstlisting}

@@

The abstract syntax can be straightforwardly described in Scala as follows:
TODO: update the abstract syntax.

@@

\section{Conclusion}\label{sec:conclusion}

@@

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

\note{TR: can this be merged with contributions? (they currently lack section refs)}
The remainder of this paper is organized as follows.
We begin by describing the target language we will analyze in Section~\ref{background},
including a concrete CESK machine as small-step operational semantics for it.
We continue with a review of abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines. Following this, Section~\ref{linear} shows a conversion from the
nondeterministic choices of closures to another layer of continuations,
therefore linearizing the abstract execution.
Section~\ref{fusing} then discusses fusing the driver and step functions to a single
function.
We further identify in Section~\ref{disen} the first-order data type representations of
continuations, and disentangle the code blocks for dispatching data types to separate
functions.
Section~\ref{refunc} then represents the refunctionalized abstract abstract machines.
In this section, the continuations represented by data types become higher-order
functions.
In Section~\ref{directstyle}, we transform the refunctionalized AAM to two
different direct style, one is implemented with monads, the other is using
delimited controls.

@@

\todo{Add section numbers to the figure}\note{TR: put this into a proper figure, add known danvy sequence 
for concrete evaluators at the bottom (in grey or dashed lines)}

@@

\begin{lstlisting}
  e $\in$ Exp ∂::= ae | (let ([x (ae ae)]) e)
 ae $\in$ AExp ::= ∂x | lam
lam $\in$ Lam ∂::= (lambda (x) e)
  x $\in$ Var   (variable names)
\end{lstlisting}

@@

The abstract syntax can be straightforwardly described in Scala as follows:
\note{TR: grammar below isn't ANF. Either make it so, or clarify that 
we assume ANF only as convention and don't need/want to enforce it in
the term structure}

@@

\section{Conclusion}\label{sec:conclusion}
\note{todo}

@@

%% Appendix
% \appendix
% \section{Appendix}

% Text of appendix \ldots
